Park Access Analysis

### 2017-10-30 R/park_ls_analysis.Rmd
This document provides the park access coefficients and significance values for all models in all cities. I note the findings that I think seem important with the hope of identifying a strong narrative that we can use to frame our paper.
Updated park access coefficients based on new model runs with updated  park data.

---
title: "Park Access Analysis"
author: "Nico Boyd"
date: "August 2, 2017"
output: html_document
---

@@

### Obesity Models
* OLS -> +0.00 (not significant)
* SAR -> -0.04 (not significant)
* SEM -> -0.01 (not significant)
* SDM -> -0.30 (not significant)  lag of park_ls = -0.13 (not significant)

### Physical Activity Models
* OLS -> -0.03 (not significant)
* SAR -> -0.04 (not significant)
* SEM -> -0.02 (not significant)
* SDM -> -0.23 (not significant)  lag of park_ls = -0.26 (not significant)

### Mental Health Models
* OLS -> +0.04 (not significant)
* SAR -> +0.02 (not significant)
* SEM -> +0.02 (not significant)
* SDM -> -0.31 (not significant)  lag of park_ls = +0.31 (not significant)

@@

### Obesity Models
* OLS -> +0.01 (not significant)
* SAR -> +0.00 (not significant)
* SEM -> +0.00 (not significant)
* SDM -> -0.08 (not significant)  lag of park_ls = -0.09 (not significant)

### Physical Activity Models
* OLS -> -0.02 (not significant)
* SAR -> -0.02 (not significant)
* SEM -> -0.02 (not significant)
* SDM -> -0.03 (not significant)  lag of park_ls = -0.19 (not significant)

### Mental Health Models
* OLS -> +0.02 (not significant)
* SAR -> +0.02 (not significant)
* SEM -> +0.01 (not significant)
* SDM -> -0.01 (not significant)  lag of park_ls = +0.05 (not significant)

@@

### Obesity Models
* OLS -> +0.01 (not significant)
* SAR -> +0.01 (not significant)
* SEM -> +0.01 (not significant)
* SDM -> -0.03 (not significant)  lag of park_ls = -0.04 (not significant)

### Physical Activity Models
* OLS -> -0.01 (not significant)
* SAR -> -0.01 (not significant)
* SEM -> -0.01 (not significant)
* SDM -> -0.00 (not significant)  lag of park_ls = -0.09 (not significant)

### Mental Health Models
* OLS -> +0.02 (not significant)
* SAR -> +0.02 (not significant)
* SEM -> +0.01 (not significant)
* SDM -> +0.02 (not significant)  lag of park_ls = +0.03 (not significant)

@@

### Obesity Models
* OLS -> +0.00 (not significant)
* SAR -> -0.04 (not significant)
* SEM -> -0.01 (not significant)
* SDM -> -0.30 (not significant)  lag of park_ls = -0.13 (not significant)

### Physical Activity Models
* OLS -> -0.03 (not significant)
* SAR -> -0.04 (not significant)
* SEM -> -0.02 (not significant)
* SDM -> -0.23 (not significant)  lag of park_ls = -0.26 (not significant)

### Mental Health Models
* OLS -> +0.04 (not significant)
* SAR -> +0.02 (not significant)
* SEM -> +0.02 (not significant)
* SDM -> -0.31 (not significant)  lag of park_ls = +0.34 (not significant)

@@

### Obesity Models
* OLS -> +0.01 (not significant)
* SAR -> +0.01 (not significant)
* SEM -> +0.01 (not significant)
* SDM -> -0.03 (not significant)  lag of park_ls = -0.04 (not significant)

### Physical Activity Models
* OLS -> -0.01 (not significant)
* SAR -> -0.01 (not significant)
* SEM -> -0.01 (not significant)
* SDM -> -0.00 (not significant)  lag of park_ls = -0.09 (not significant)

### Mental Health Models
* OLS -> +0.02 (not significant)
* SAR -> +0.02 (not significant)
* SEM -> +0.01 (not significant)
* SDM -> +0.02 (not significant)  lag of park_ls = +0.03 (not significant)

@@

### Obesity Models
* OLS -> -0.74 (**significant at 0.001**)
* SAR -> -0.76 (**significant at 0.001**)
* SEM -> -0.12 (not significant)
* SDM -> +0.04 (not significant)  lag of park_ls = -0.43 (**significant at 0.001**)

  > *As my neighbors' park access decreases, I become more obese. Conversely, as my neighbors get better access to         parks, I become less obese. This spatial durbin model of obesity is the most likely in NYC.*

### Physical Activity Models
* OLS -> -0.05 (not significant)
* SAR -> -0.16 (not significant)
* SEM -> -0.02 (not significant)
* SDM -> +0.05 (not significant)  lag of park_ls = -0.15 (not significant)

@@

### Obesity Models
* OLS -> -0.74 (**significant at 0.001**)
* SAR -> -0.76 (**significant at 0.001**)
* SEM -> -0.12 (not significant)
* SDM -> +0.04 (not significant)  lag of park_ls = -0.43 (**significant at 0.01**)

### Physical Activity Models
* OLS -> -0.05 (not significant)
* SAR -> -0.16 (not significant)
* SEM -> -0.02 (not significant)
* SDM -> +0.05 (not significant)  lag of park_ls = -0.15 (not significant)

>>>>

---
title: "Park Access Analysis"
author: "Nico Boyd"
date: "October 22, 2017"
output: html_document
---

@@

### Obesity Models
* OLS -> +0.06 (not significant)
* SAR -> +0.01 (not significant)
* SEM -> +0.05 (not significant)
* SDM -> -0.28 (not significant)  lag of park_ls = -0.12 (not significant)

### Physical Activity Models
* OLS -> +0.00 (not significant)
* SAR -> -0.02 (not significant)
* SEM -> +0.01 (not significant)
* SDM -> -0.24 (not significant)  lag of park_ls = -0.28 (not significant)

### Mental Health Models
* OLS -> +0.08 (not significant)
* SAR -> +0.06 (not significant)
* SEM -> +0.06 (not significant)
* SDM -> -0.21 (not significant)  lag of park_ls = +0.24 (not significant)

@@

### Obesity Models
* OLS -> +0.03 (not significant)
* SAR -> +0.02 (not significant)
* SEM -> +0.02 (not significant)
* SDM -> -0.09 (not significant)  lag of park_ls = -0.07 (not significant)

### Physical Activity Models
* OLS -> -0.03 (not significant)
* SAR -> -0.03 (not significant)
* SEM -> -0.03 (not significant)
* SDM -> -0.05 (not significant)  lag of park_ls = -0.17 (not significant)

### Mental Health Models
* OLS -> +0.02 (not significant)
* SAR -> +0.01 (not significant)
* SEM -> +0.01 (not significant)
* SDM -> -0.01 (not significant)  lag of park_ls = +0.05 (not significant)

@@

### Obesity Models
* OLS -> +0.02 (not significant)
* SAR -> +0.01 (not significant)
* SEM -> +0.01 (not significant)
* SDM -> -0.04 (not significant)  lag of park_ls = -0.03 (not significant)

### Physical Activity Models
* OLS -> -0.01 (not significant)
* SAR -> -0.01 (not significant)
* SEM -> -0.01 (not significant)
* SDM -> -0.00 (not significant)  lag of park_ls = -0.08 (not significant)

### Mental Health Models
* OLS -> +0.01 (not significant)
* SAR -> +0.01 (not significant)
* SEM -> +0.00 (not significant)
* SDM -> +0.00 (not significant)  lag of park_ls = +0.03 (not significant)

@@

### Obesity Models
* OLS -> +0.06 (not significant)
* SAR -> +0.01 (not significant)
* SEM -> +0.05 (not significant)
* SDM -> -0.28 (not significant)  lag of park_ls = -0.12 (not significant)

### Physical Activity Models
* OLS -> +0.00 (not significant)
* SAR -> -0.02 (not significant)
* SEM -> +0.01 (not significant)
* SDM -> -0.24 (not significant)  lag of park_ls = -0.28 (not significant)

### Mental Health Models
* OLS -> +0.08 (not significant)
* SAR -> +0.06 (not significant)
* SEM -> +0.06 (not significant)
* SDM -> -0.21 (not significant)  lag of park_ls = +0.24 (not significant)

@@

### Obesity Models
* OLS -> +0.02 (not significant)
* SAR -> +0.01 (not significant)
* SEM -> +0.01 (not significant)
* SDM -> -0.04 (not significant)  lag of park_ls = -0.03 (not significant)

### Physical Activity Models
* OLS -> -0.02 (not significant)
* SAR -> -0.02 (not significant)
* SEM -> -0.02 (not significant)
* SDM -> -0.02 (not significant)  lag of park_ls = -0.08 (not significant)

### Mental Health Models
* OLS -> +0.01 (not significant)
* SAR -> +0.01 (not significant)
* SEM -> +0.00 (not significant)
* SDM -> +0.00 (not significant)  lag of park_ls = +0.03 (not significant)

@@

### Obesity Models
* OLS -> -0.74 (**significant at 0.001**)
* SAR -> -0.76 (**significant at 0.001**)
* SEM -> -0.12 (not significant)
* SDM -> +0.04 (not significant)  lag of park_ls = -0.43 (**significant at 0.05**)

  > *The OLS and SAR models indicate that as my access to parks improves, I become less obese. According to the SDM model, as my neighbors' park access decreases, I become more obese. Conversely, as my neighbors get better access to parks, I become less obese. This spatial durbin model of obesity is the most likely in NYC.*

### Physical Activity Models
* OLS -> -0.05 (not significant)
* SAR -> -0.16 (not significant)
* SEM -> -0.02 (not significant)
* SDM -> +0.05 (**significant at 0.001**)  lag of park_ls = -0.15 (not significant)

> *The SDM model indicates that I become less active as my access to parks improves.*

### Mental Health Models
* OLS -> -0.01 (not significant)
* SAR -> -0.06 (not significant)
* SEM -> +0.01 (not significant)
* SDM -> -0.08 (**significant at 0.001**)  lag of park_ls = +0.03 (not significant)

> *The SDM model indicates that my self-reported mental health becomes better as my access to parks improves.*

@@

### Obesity Models
* OLS -> -0.74 (**significant at 0.001**)
* SAR -> -0.76 (**significant at 0.001**)
* SEM -> -0.12 (not significant)
* SDM -> +0.04 (not significant)  lag of park_ls = -0.43 (not significant)

  > *The OLS and SAR models indicate that I become less obese as my access to parks improves.*

### Physical Activity Models
* OLS -> -0.05 (not significant)
* SAR -> -0.16 (**significant at 0.05**)
* SEM -> -0.02 (not significant)
* SDM -> +0.05 (not significant)  lag of park_ls = -0.15 (not significant)

> *The SAR model indicates that I become less obese as my access to parks improves.*
